---
title: "R course presentation"
author: "Rain Inno"
date: "2017/11/29"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

class: left, top

# Questions that need an answer

### 1. Is mircoRNA expression correlated with other microRNAs?
### 2. What are the genes that these microRNAs regulate?

---
class: left, top

# Used dataset

### 1. MicroRNA sequences n=50
### 2. RNA sequences n=1000


---
class: left, top

# Used packages

* dplyr
* tidyverse
* stringr
* data.table
* ggplot2
* DESeq2

```{r, echo=FALSE, error=FALSE, message=FALSE, gache=FALSE}
library(dplyr)
library(tidyverse)
library(stringr)
require(DESeq2) #analysis itself
library(data.table)
library(ggplot2)
library(gridExtra)


mirna_hor=read.table("mirna_hor.txt", sep="\t", header=T)
mirna_ver<-read.table("mirna_ver.txt",header=T)
gene_ver<-read.table("gene_ver.txt", header=T)
gene_hor = t(gene_ver)


```

---
Using DESeq2 for expression correlation analysis
```yaml

 colNR=2
 for(i in row.names(mirna_hor)){
   for(j in row.names(mirna_ver)){
     colNR=colNR+1
     b<-colnames(mirna_hor[colNR])
     testTable=data.frame(mirna_hor[,colNR],mirna_hor$type)
     a<-str_replace(j,"-",".")
     colnames(testTable)=c("mirna","type")
     dds=DESeqDataSetFromMatrix(countData=mirna_ver, colData=testTable, design=~type+mirna)
     dds=DESeq(dds,test="LRT",reduced=~1)
     ddsReplace <- replaceOutliers(dds)
     ddsReplace <- DESeq(ddsReplace)
     res=results(ddsReplace)
     write.table(res, file=paste0("mirna_",b,"_test_DESeq2.txt"))
     print(b)
   }
 }

```

---
Combine all results files

```yaml
 failid=list.files()
 koik_andmed=read.table(fail, header=T)
 for (fail in failid) {
   id=unlist(strsplit(fail, "[_]"))[2]
   print(id)
   andmed=read.table(fail, header=T)
   colnames(andmed)[colnames(andmed)=="padj"]<-id
   koik_andmed=cbind(koik_andmed, andmed[6])
 }
 
 write.table(koik_andmed, "mir_mir_koos.tsv", sep="\t", row.names=T, quote=F)
 
mir_mir <- read.table("mir_mir_koos.tsv", head=T)
mir_mir <- mir_mir[!(names(mir_mir) %in% c("baseMean", "log2FoldChange", "lfcSE", "stat", "pvalue", "padj"))]
mir_mir <- setDT(mir_mir, keep.rownames = T)
```
```{r, echo=FALSE}

mir_mir <- read.table("mir_mir_koos.tsv", head=T)
mir_mir <- mir_mir[!(names(mir_mir) %in% c("baseMean", "log2FoldChange", "lfcSE", "stat", "pvalue", "padj"))]
mir_mir <- setDT(mir_mir, keep.rownames = T)
print(mir_mir[1:5,1:5])


```

---
How many microRNAs expression is correlated

```{r, error=TRUE}

colSums(mir_mir < 0.00005)

```
---
Arrenge by most interesting microRNA

```{r, error=TRUE}

mir_mir<-arrange(mir_mir, miR.003)

mir_mir[1:10,1]

```


---

```{r,echo=FALSE}

top_mirna <- mirna_hor[mir_mir[1,1]]


top10 <- mir_mir[1:10,1]
top10_2 <- mirna_hor[,mir_mir[2,1]]
top10_3 <- mirna_hor[,mir_mir[3,1]]
top10_4 <- mirna_hor[,mir_mir[4,1]]
top10_5 <- mirna_hor[,mir_mir[5,1]]
top10_6 <- mirna_hor[,mir_mir[6,1]]
top10_7 <- mirna_hor[,mir_mir[7,1]]
top10_8 <- mirna_hor[,mir_mir[8,1]]
top10_9 <- mirna_hor[,mir_mir[9,1]]
top10_10 <- mirna_hor[,mir_mir[10,1]]


p1 <- mirna_hor %>% ggplot(aes(top_mirna, top10_2 	))+geom_point()+geom_smooth(method="lm")
p2 <- mirna_hor %>% ggplot(aes(top_mirna, top10_3 	))+geom_point()+geom_smooth(method="lm")
p3 <- mirna_hor %>% ggplot(aes(top_mirna, top10_4 	))+geom_point()+geom_smooth(method="lm")
p4 <- mirna_hor %>% ggplot(aes(top_mirna, top10_5 	))+geom_point()+geom_smooth(method="lm")
p5 <- mirna_hor %>% ggplot(aes(top_mirna, top10_6 	))+geom_point()+geom_smooth(method="lm")
p6 <- mirna_hor %>% ggplot(aes(top_mirna, top10_7 	))+geom_point()+geom_smooth(method="lm")
p7 <- mirna_hor %>% ggplot(aes(top_mirna, top10_8 	))+geom_point()+geom_smooth(method="lm")
p8 <- mirna_hor %>% ggplot(aes(top_mirna, top10_9 	))+geom_point()+geom_smooth(method="lm")
p9 <- mirna_hor %>% ggplot(aes(top_mirna, top10_10 	))+geom_point()+geom_smooth(method="lm")

```

```{r, echo=FALSE, error=TRUE, message=FALSE, fig.width=12, fig.height=8}

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9,ncol=3)

```

---

```{r, echo=FALSE}

mir_gene <- read.table("mir_gene_koos.tsv", head=T, sep="\t")
mir_gene=mir_gene[!(names(mir_gene) %in% c("baseMean", "log2FoldChange", "lfcSE", "stat", "pvalue", "padj"))]
mir_gene <- setDT(mir_gene, keep.rownames = T)
rn<-mir_gene$rn
print(mir_gene[1:5,1:5])


```

---
How many microRNA and genes expression is correlated

```{r, error=TRUE}

colSums(mir_gene < 0.005)

```
---
Arrenge by most interesting microRNA

```{r, error=TRUE}

mir_gene<-arrange(mir_gene, miR.003)

mir_gene[1:10,1]

```

---

```{r,echo=FALSE, messages=FALSE}

top10_2 <- gene_hor[,mir_gene[1,1]]
top10_3 <- gene_hor[,mir_gene[2,1]]
top10_4 <- gene_hor[,mir_gene[3,1]]
top10_5 <- gene_hor[,mir_gene[4,1]]
top10_6 <- gene_hor[,mir_gene[5,1]]
top10_7 <- gene_hor[,mir_gene[6,1]]
top10_8 <- gene_hor[,mir_gene[7,1]]
top10_9 <- gene_hor[,mir_gene[8,1]]
top10_10 <- gene_hor[,mir_gene[9,1]]


p1 <- mirna_hor %>% ggplot(aes(top_mirna, top10_2 	))+geom_point()+geom_smooth(method="lm")
p2 <- mirna_hor %>% ggplot(aes(top_mirna, top10_3 	))+geom_point()+geom_smooth(method="lm")
p3 <- mirna_hor %>% ggplot(aes(top_mirna, top10_4 	))+geom_point()+geom_smooth(method="lm")
p4 <- mirna_hor %>% ggplot(aes(top_mirna, top10_5 	))+geom_point()+geom_smooth(method="lm")
p5 <- mirna_hor %>% ggplot(aes(top_mirna, top10_6 	))+geom_point()+geom_smooth(method="lm")
p6 <- mirna_hor %>% ggplot(aes(top_mirna, top10_7 	))+geom_point()+geom_smooth(method="lm")
p7 <- mirna_hor %>% ggplot(aes(top_mirna, top10_8 	))+geom_point()+geom_smooth(method="lm")
p8 <- mirna_hor %>% ggplot(aes(top_mirna, top10_9 	))+geom_point()+geom_smooth(method="lm")
p9 <- mirna_hor %>% ggplot(aes(top_mirna, top10_10 	))+geom_point()+geom_smooth(method="lm")

```

```{r, echo=FALSE, error=TRUE, message=FALSE, fig.width=12, fig.height=8}

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, ncol=3)

```
---

```yaml
mirnaNR=0

for(i in row.names(mirna_ver)){
  mirnaNR=mirnaNR+1
  print(mirnaNR)
  sink(paste0("geen_",i,"_test_pearson.txt"),type="output")
  print(i)
  for(j in row.names(gene_ver)){
    suhe.lm=cor(as.numeric(mirna_ver[i,]), as.numeric(gene_ver[j,],method="pearson"))
    print(suhe.lm)
  }
  sink()
}
```


```{r, echo=FALSE}

mir_gene_pearson <- read.table("mir_gene_pearson_koos.tsv", head=T, sep="\t")
mir_gene_pearson=mir_gene_pearson[!(names(mir_gene_pearson) %in% c("X.1.", "miR.001.1"))]
mir_gene_pearson <- setDT(mir_gene_pearson, keep.rownames = T)
mir_gene_pearson$rn <- rn

head(mir_gene_pearson[1:5,1:5])


```

---
How many microRNA and genes expression is negatively correlated

```{r, error=TRUE}

colSums(mir_gene_pearson < 0)

```
---
Arrenge by most interesting microRNA

```{r, error=TRUE}

mir_gene_pearson<-arrange(mir_gene_pearson, miR.003)

mir_gene_pearson[1:10,1:4]

```

---

```{r,echo=FALSE, messages=FALSE}

top10_2 <- gene_hor[,mir_gene_pearson[1,1]]
top10_3 <- gene_hor[,mir_gene_pearson[2,1]]
top10_4 <- gene_hor[,mir_gene_pearson[3,1]]
top10_5 <- gene_hor[,mir_gene_pearson[4,1]]
top10_6 <- gene_hor[,mir_gene_pearson[5,1]]
top10_7 <- gene_hor[,mir_gene_pearson[6,1]]
top10_8 <- gene_hor[,mir_gene_pearson[7,1]]
top10_9 <- gene_hor[,mir_gene_pearson[8,1]]
top10_10 <- gene_hor[,mir_gene_pearson[9,1]]


p1 <- mirna_hor %>% ggplot(aes(top_mirna, top10_2 	))+geom_point()+geom_smooth(method="lm")
p2 <- mirna_hor %>% ggplot(aes(top_mirna, top10_3 	))+geom_point()+geom_smooth(method="lm")
p3 <- mirna_hor %>% ggplot(aes(top_mirna, top10_4 	))+geom_point()+geom_smooth(method="lm")
p4 <- mirna_hor %>% ggplot(aes(top_mirna, top10_5 	))+geom_point()+geom_smooth(method="lm")
p5 <- mirna_hor %>% ggplot(aes(top_mirna, top10_6 	))+geom_point()+geom_smooth(method="lm")
p6 <- mirna_hor %>% ggplot(aes(top_mirna, top10_7 	))+geom_point()+geom_smooth(method="lm")
p7 <- mirna_hor %>% ggplot(aes(top_mirna, top10_8 	))+geom_point()+geom_smooth(method="lm")
p8 <- mirna_hor %>% ggplot(aes(top_mirna, top10_9 	))+geom_point()+geom_smooth(method="lm")
p9 <- mirna_hor %>% ggplot(aes(top_mirna, top10_10 	))+geom_point()+geom_smooth(method="lm")

```

```{r, echo=FALSE, error=TRUE, message=FALSE, fig.width=12, fig.height=8}

grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, ncol=3)

```
---